\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-10 paper.tex
Correct small mistake
Some corrections, describe new figures, upt to sec. 3.1

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \caption{Top view of the electrolytic cell (light blue) showing the charge at the

@@

    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
    $y=0,b$. The relation of some charges and their images is

@@

  \caption{Side view of the electrolytic cell (light blue)

@@

    dots). We use solid dots to denote particles with the same charge
    as that corresponding to the tip $q_0$, and open dots for those of
    opposite charge. The system may be interpreted as a periodic

@@

Each plane of charges upon reflection on the surface of the sample yields an

@@

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{(a) \notaL{reordenar figura} Experimental set-up for
      fabrication of porous silicon with GRIN, consisting of a
      rectangular electrochemical cell. We indicate the Si wafer, the
      teflon cell, the platinum point electrode, the electrolyte and the
      current source. (b) Top and (c) side schematic views of the resulting sample,
      illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
      low porosity respectively illustrating the change gradient in
      pore size and depth. }}
    \label{fig:DE1}
  \end{figure}

Fig. \ref{fig:DE1} shows a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{La figura está feita. Hay un abultamiento extraño en la
  punta. Debería verse el aislamiento y la punta descubierta y más
  sumergida. La letra está demasiado chica. El gradiente de porosidad va
  en la dirección opuesta. El panel (a) tiene una discontinuidad. ¿Tú
  la hiciste o la adaptaste? Usa dos paréntesis (a), (b),
  (c). Alínealos. Pon primero la preparación y luego los resultados
  vistos de arriba y de lado. Está en desorden. Se ve muy descuidada. No dice nada sobre la
  preparación que no esté en la figura 1. Dos páneles no ilustran el
  método experimental, sino el resultado. Quizás yo la quitaría.}
taking into account the considerations of the electrode as tip, the
rectangular cell and the sample (silicon wafer) with the largest
rectangular attack area.

In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
divided by three regions A, B and C, dependes in therir porosity i.e.,
High, Medium and Low Porosity. All this corresponding to  expected to
be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
the electrochemical cell with its parts: silicon wafer, teflon cell,
platinum point electrode, electrochemical Aqueous Solution and the
connection of the circuit with the cathode and anode. Finally,
Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
of the electrochemically attacked porous silicon seen from three
different regions as mentioned above. In section 3.1 we give the
details used to carry out our experiments.

>>>>

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \caption{Top view of the fictitious system formed by reflections of
    the electrolytic cell (light blue) showing the charge at the

@@

    rectangular cell, the images of its images and so on (blue
    dots). The walls are at $x=0,a$,
    $y=0,b$ (blue lines). The relation of some charges and their images is

@@

  \caption{Side view of the fictitious system formed by reflections of
    the electrolytic cell (light blue)

@@

    dots). We use solid dots to denote images with the same charge $q_0$
    as that corresponding to the tip of the electrode, and open dots for those of
    opposite charge $-q_0$. The mirror planes that don't invert the charge
    are indicated by blue lines and the mirror plane that inverts the
    charge is indicated by a red line. The relation of some charges and their images is
    corresponding reflecting wall. The system may be interpreted as a periodic

@@

Each plane of charges upon reflection on the surface of the sample at
the bottom of the cell yields an

@@

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}
  %\\[12pt]
  %\includegraphics[scale=0.6]{Images/DE1}

\caption{\notaL{reordené figura y rehice} Experimental set-up for
      the fabrication of porous silicon with GRIN, consisting of a
      rectangular electrochemical cell. We indicate the Si wafer (dark
      gray), the teflon cell (light gray), the sealing o-ring (black
      circles), the insulated feeding cable (white lines within black
      lines), the uncovered platinum tip (white) within the
      electrolyte (blue), the electrical contact below the sample
      (yellow) and the current source. We indicate some geometrical
      parameters of the arrangement $x0$, $z0$, $a$ and $c$
      and the current source (upper panel) and a few current density
      field lines. Top (middle panel) and
      side (lower panel) schematic views of the resulting sample,
      illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
      low porosity respectively illustrating the gradients in pore
      size, density and depth. \notaL{Es $\nabla p$ razonable para el
        gradiente de la porosidad}}
    \label{fig:DE1}
  \end{figure}

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras} \notaL{La figura está feita. Hay un abultamiento extraño en la
  punta. Debería verse el aislamiento y la punta descubierta y más
  sumergida. La letra está demasiado chica. El gradiente de porosidad va
  en la dirección opuesta. El panel (a) tiene una discontinuidad. ¿Tú
  la hiciste o la adaptaste? Usa dos paréntesis (a), (b),
  (c). Alínealos. Pon primero la preparación y luego los resultados
  vistos de arriba y de lado. Está en desorden. Se ve muy descuidada. No dice nada sobre la
  preparación que no esté en la figura 1. Dos páneles no ilustran el
  método experimental, sino el resultado. Quizás yo la quitaría.}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si which makes an
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.
